\section{Email marketing tool Requirements}

This section outlines the requirements for an email marketing tool. The tool is designed to meet the needs of various actors. The requirements are divided into functional and non-functional requirements, providing a comprehensive overview of what the system is expected to do and the standards it should adhere to.

\subsection{Identification of the actors}
The system will interact with the following actors:
\begin{itemize}
\item \textbf{New User}: A person who has not registered an account yet.
\item \textbf{User}: A person who has registered an account and can log in.
\item \textbf{Administrator}: A user who has created an organization and manages it.
\end{itemize}

\subsection{Functional Requirements}

\subsubsection{New Users}
\begin{itemize}
    \item \textbf{Account Registration}
\end{itemize}

\subsubsection{Users}
\begin{itemize}
\item \textbf{Account Login}
\item \textbf{Organization Creation}
\item \textbf{Organization List View}
\item \textbf{Email Template Creation}
\item \textbf{Email Template Editing}
\item \textbf{Email Template List View}
\item \textbf{Email Template Search}
\item \textbf{Draft Management}
\item \textbf{Email Sending}
\item \textbf{Sent Email History}
\item \textbf{Campaign Creation}
\item \textbf{Campaign Management}
\item \textbf{Campaign List View}
\item \textbf{Campaign Reports}:
\end{itemize}

\subsubsection{Administrators}
\begin{itemize}
\item \textbf{User Deactivation/Removal}
\item \textbf{User Addition and Role Assignment}
\item \textbf{Role Management}
\end{itemize}


\subsection{Non-functional requirements}
The non-functional requirements of the system are as follows:
\begin{itemize}
\item \textbf{Security}: The system should securely store user credentials and personal information. It should also provide secure access control mechanisms.
\item \textbf{Usability}: The system should be user-friendly, allowing users to easily navigate and manage their organizations and email templates.
\item \textbf{Performance}: The system should provide fast and efficient access to the shared work within an organization.
\item \textbf{Reliability}: The system should reliably deliver emails and track their status and timestamp.
\item \textbf{Scalability}: The system should be able to handle a large number of users, organizations, and email templates without performance degradation.
\item \textbf{Maintainability}: The system should be easy to update and maintain, allowing for the addition of new features and updates to existing ones.
\end{itemize}
