\chapter*{Acknowledgments}


I would like to express my deepest gratitude to those who have played a pivotal role in the completion of this project. Their support, guidance, and encouragement have been invaluable, and I am eternally grateful.
\vspace{10pt}

First and foremost, I extend my sincerest thanks to Mr.Yamen Mkaddem, my academic advisor. Your unwavering support, insightful feedback, and expert guidance have been instrumental in shaping this work. Your dedication to excellence and your passion for knowledge have inspired me throughout this journey.
\vspace{10pt}

I am profoundly grateful to Mr.Raed Bahri, my professional advisor. Your practical insights, profound expertise, and continuous encouragement have significantly enriched my learning experience. Your mentorship has been a cornerstone of my professional development, and your belief in my capabilities has been a source of great motivation.
\vspace{10pt}

A special mention goes to Madam Feyrouz Hamdaoui, whose experience and wisdom have been a guiding light. Your generous sharing of knowledge, thoughtful advice, and unwavering support have been truly invaluable. Your contributions have significantly enhanced the quality of this work, and for that, I am deeply thankful.
\vspace{10pt}

To all my colleagues and friends who have provided support and feedback, your contributions have been essential. Your camaraderie and encouragement have made this journey enjoyable and fulfilling.
\vspace{10pt}

Finally, I would like to thank my family for their unwavering love and support, without which none of this would have been possible.
\vspace{10pt}

To Mr.Yamen Mkaddem,Mr. Raed Bahri, and Madam Feyrouz Hamdaoui, your guidance and support will be remembered with deep gratitude for the rest of my life. Thank you for believing in me and for helping me achieve this milestone.
