\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\markboth{General Conclusion}{General Conclusion}

Throughout this document, we meticulously outlined the backlogs for the initial three sprints of our email marketing tool project, accompanied by detailed diagrams, descriptions, and screenshots. Each sprint focused on developing essential features to build a robust application.

\vspace{10pt}

Sprint 1 established foundational features like user registration, authentication, and the email builder. The use case diagrams, textual descriptions, and implementation screenshots provided clarity on user interactions and system structure.

\vspace{10pt}

Sprint 2 enhanced organizational capabilities and collaboration through organization creation, workspace setup, and user invitations. Detailed diagrams and descriptions visualized the collaborative environment, while implementation screenshots showcased user interface improvements.

\vspace{10pt}

Sprint 3 implemented advanced tracking features and a CI/CD pipeline for automated deployment. Use case diagrams and descriptions clarified tracking processes, while design diagrams detailed technical aspects. Implementation screenshots highlighted tracking features and dashboard functionalities.

\vspace{10pt}

The structured approach in each sprint backlog, coupled with comprehensive documentation, ensures clarity in task responsibilities. This methodology fosters efficient teamwork and progress. We are poised to deliver a comprehensive email marketing tool meeting user needs and expectations.
