\section{Sprint 1 Backlog}

The table below outlines the tasks planned for Sprint 1. This sprint focuses on the development of key features for the email marketing tool, including the email builder, email sending functionalities, and user registration and authentication.

\begin{longtable}{|c|p{0.83\textwidth}|}
	\hline
	\textbf{ID} & \textbf{Task Description}                                                                                                         \\
	\hline
	1           & Create a user registration system, including the interface and backend functionality for new users to sign up.                    \\
	\hline
	2           & Implement user authentication, enabling registered users to log in securely.                                                      \\
	\hline
	3           & Enable access to shared resources (templates, campaigns, media) within an organization, promoting effective collaboration.        \\
	\hline
	4           & Implement the email builder feature. This involves creating the user interface and functionality for customizing email templates. \\
	\hline
	5           & Create customizable email templates for various communication needs.                                                              \\
	\hline
	6           & Enable users to edit and update email templates to keep information accurate and relevant.                                        \\
	\hline
	7           & Allow users to create and manage email template drafts before finalizing and sending.                                             \\
	\hline
	8           & Develop the email sending logic, allowing users to send emails using selected templates to specified recipients.                  \\
	\hline
	9           & Implement campaign creation and publishing using selected templates.                                                              \\
	\hline
	10          & Maintain a history of published campaigns for reference and analysis.                                                             \\
	\hline
	\caption{Sprint 1 Backlog}
	\label{tab
	}
\end{longtable}


The structured approach outlined in this backlog ensures clarity in understanding the responsibilities and the goals for this sprint.
